Simulating Ultra High-Dimensional Multivariate Data Using the bigsimr R Package

### 2020-10-21 070-supplementary-materials.Rmd
push small change after meeting
added chapter prefix

# Notes

### List of supported distributions

```{r, eval=FALSE}
all_dists <- list(
  list(dist = "beta", shape1, shape2),
  list(dist = "binom", size, prob),
  list(dist = "cauchy", location, scale),
  list(dist = "chisq", df),
  list(dist = "exp", rate),
  list(dist = "f", df1, df2),
  list(dist = "gamma", shape, rate),
  list(dist = "geom", prob),
  list(dist = "hyper", m, n, k),
  list(dist = "logis", location, scale),
  list(dist = "lnorm", meanlog, sdlog),
  list(dist = "nbinom", size, prob),
  list(dist = "norm", mean, sd),
  list(dist = "pois", lambda),
  list(dist = "t", df),
  list(dist = "unif", min, max),
  list(dist = "weibull", shape, scale),
  list(dist = "wilcox", m, n),
  list(dist = "signrank", n)
)
```

Mention Python?

>>>>

```{r ch070-all-dists, eval=FALSE}
all_dists <- list(
  list(dist = "beta", shape1, shape2),
  list(dist = "binom", size, prob),
  list(dist = "cauchy", location, scale),
  list(dist = "chisq", df),
  list(dist = "exp", rate),
  list(dist = "f", df1, df2),
  list(dist = "gamma", shape, rate),
  list(dist = "geom", prob),
  list(dist = "hyper", m, n, k),
  list(dist = "logis", location, scale),
  list(dist = "lnorm", meanlog, sdlog),
  list(dist = "nbinom", size, prob),
  list(dist = "norm", mean, sd),
  list(dist = "pois", lambda),
  list(dist = "t", df),
  list(dist = "unif", min, max),
  list(dist = "weibull", shape, scale),
  list(dist = "wilcox", m, n),
  list(dist = "signrank", n)
)
```
